### 2019-07-25 2_task_bench.tex
Changes to trim word count.
Apply Alex's updates.

Dependencies between tasks are controlled by a configurable dependence
relation. The
dependence relation enumerates the set of tasks from the
previous time step each task depends on. This permits a wide variety
of dependence patterns to be implemented that are relevant to real
applications in high-performance scientific computing and data analysis: stencils,
sweeps, FFTs, trees, etc. Dependence patterns may also be
parameterized, such as picking the $K$ nearest neighbors, or $K$
distant neighbors. Table~\ref{tab:equations} show equations for the
dependence relations of the patterns in Figure~\ref{fig:task-graphs},
where $t$ is timestep, $i$ is column, and $W$ is the width of the task
graph.

@@

The Task Bench core library is fully
validating. Because the task graph configuration is explicitly
represented (though unmaterialized) in Task Bench, this representation
can be queried to determine exactly what dependencies a task should
expect. The output of every task in Task Bench is unique,
and all inputs are verified. An assertion is thrown if validation
fails. This level of self-checking ensures that every execution of Task Bench, if it
completes successfully, is correct. An evaluation of the performance impact of
validation showed it to be less than 3\% at the smallest task
granularities in any Task Bench implementation, with a negligible
effect on overall results.

>>>>

Dependencies between tasks are controlled by a configurable dependence
relation. The
dependence relation enumerates the set of tasks from the
previous time step each task depends on. This permits a wide variety
of dependence patterns to be implemented that are relevant to real
applications in high-performance scientific computing and data analysis: stencils,
sweeps, FFTs, trees, etc. Dependence patterns may also be
parameterized, such as picking the $K$ nearest neighbors, or $K$
distant neighbors. Table~\ref{tab:equations} shows equations for the
dependence relations of the patterns in Figure~\ref{fig:task-graphs},
where $t$ is timestep, $i$ is column, and $W$ is the width of the task
graph.

@@

The Task Bench core library is fully
validating. Because the task graph configuration is explicitly
represented (though unmaterialized) in Task Bench, this representation
can be queried to determine exactly what dependencies a task should
expect. The output of every task in Task Bench is unique,
and all inputs are verified. An assertion is thrown if validation
fails. These checks ensure that every execution of Task Bench, if it
completes successfully, is correct. An evaluation of the performance impact of
validation showed it to be less than 3\% at the smallest task
granularities in any Task Bench implementation, with a negligible
effect on overall results.

### 2019-07-25 4_metg.tex
Apply Alex's updates.

Existing studies which consider programming system efficiency
typically use the metric \emph{tasks per second} (TPS). TPS results
are difficult to interpret and apply, because the efficiency (and thus
the amount of useful work) is not constrained. When using empty
tasks~\cite{LegionTracing18}, the resulting upper bound on task
scheduling throughput fails to represent useful work within a
realistic application. With non-empty tasks, since the efficiency of
the overall application is typically not reported~\cite{Canary16,
  Armstrong14}, TPS is not a measurement of runtime-limited
performance. Large tasks may be used to hide any amount of runtime
overhead, while small tasks may result in a drop in total application
throughput even as TPS increases.

@@

METG(50\%) is the intersection of this curve with 50\% efficiency, as
shown by the red, dashed lines in Figure~\ref{fig:flops-mpi} and
\ref{fig:efficiency-mpi}. At 50\% efficiency, MPI achieves an average
task granularity of
4.6 \textmu{}s, thus the METG(50\%) of MPI is 4.6 \textmu{}s in this
configuration. We use 50\% because that is generally an acceptable level
of efficiency in practice, and values above 90\% can misrepresent the
performance of some systems (see
Section~\ref{subsec:peak-performance-and-efficiency}).

>>>>

Existing studies of programming system efficiency
typically use the metric \emph{tasks per second} (TPS). TPS results
are difficult to interpret and apply, because the efficiency (and thus
the amount of useful work) is not constrained. When using empty
tasks~\cite{LegionTracing18}, the resulting upper bound on task
scheduling throughput fails to represent useful work within a
realistic application. With non-empty tasks, since the efficiency of
the overall application is typically not reported~\cite{Canary16,
  Armstrong14}, TPS is not a measurement of runtime-limited
performance. Large tasks may be used to hide any amount of runtime
overhead, while small tasks may result in a drop in total application
throughput even as TPS increases.

@@

METG(50\%) is the intersection of this curve with 50\% efficiency, as
shown by the red, dashed lines in Figures~\ref{fig:flops-mpi} and
\ref{fig:efficiency-mpi}. At 50\% efficiency, MPI achieves an average
task granularity of
4.6 \textmu{}s, thus the METG(50\%) of MPI is 4.6 \textmu{}s in this
configuration. We use 50\% because that is generally an acceptable level
of efficiency in practice, and values above 90\% can misrepresent the
performance of some systems (see
Section~\ref{subsec:peak-performance-and-efficiency}).

### 2019-07-25 5_evaluation.tex
Apply Alex's updates.

\input{e1_flops}
\input{e2_efficiency}

@@

METG is a useful metric in part because it summarizes the basic task
scheduling overhead of each programming system in a single number. This makes it
possible to evaluate METG at different node counts (shown in
Figure~\ref{fig:metg-compute}) to see how it is impacted by changes in
communication topology and latency. An interesting observation is that
the systems with the smallest METG on one node have roughly an order
of magnitude higher METG at 256 nodes---increased communication latencies require significantly larger tasks to
achieve the same level of efficiency.

@@

Our MPI+CUDA implementation uses an offload model in which input and
output data is copied to and from the GPU on each time step. We tested
two configurations: \lstinline{w1} uses 1 task per GPU, whereas
\lstinline{w4} overdecomposes by a factor of $4\times$, using 4 MPI
ranks per GPU to push work to the GPU in parallel and thus overlaps communication and computation. We see that the
\lstinline{w4} configuration achieves higher FLOP/s but
drops more rapidly at smaller problem sizes, due to the overhead of
scheduling $4\times$ as many CUDA kernel launches. In either case, the
GPU requires more work to achieve high performance, and the overhead
of copying data to and from the GPU dominates at small task
granularities, where the CPU achieves higher
performance. While Figure~\ref{fig:cuda-efficiency} is not couched in
terms of MTEG (as the peak performance of the GPU and CPU are very
different), the conclusion here is similar to
Section~\ref{subsec:scalability}: The cost of communicating data and
tasks to and from the GPU imposes a higher task granularity to achieve
the same efficiency than running on the CPU, reducing the advantage of
very lightweight mechanisms such as those in MPI.

>>>>

\input{e1_flops}
\input{e2_efficiency}
\input{e7_bytes}

@@

METG is a useful metric in part because it summarizes the basic task
scheduling overhead of each programming system in a single number. This makes it
possible to evaluate METG at different node counts (shown in
Figure~\ref{fig:metg-compute}) to see how it is impacted by changes in
communication topology and latency. A key finding is that
the systems with the smallest METG on one node have roughly an order
of magnitude higher METG at 256 nodes---increased communication latencies require significantly larger tasks to
achieve the same level of efficiency, so apparent differences in
runtime overhead at small node counts can matter much less or not at
all at larger node counts.

@@

Our MPI+CUDA implementation uses an offload model in which input and
output data is copied to and from the GPU on each time step. We tested
two configurations: \lstinline{w1} uses 1 task per GPU, whereas
\lstinline{w4} overdecomposes by a factor of $4\times$, using 4 MPI
ranks per GPU to push work to the GPU in parallel and thus overlaps communication and computation. We see that the
\lstinline{w4} configuration achieves higher FLOP/s but
drops more rapidly at smaller problem sizes, due to the overhead of
scheduling $4\times$ as many CUDA kernel launches. In either case, the
GPU requires more work to achieve high performance, and the overhead
of copying data to and from the GPU dominates at small task
granularities, where the CPU achieves higher
performance. While Figure~\ref{fig:cuda-efficiency} is not couched in
terms of MTEG (as the peak performance of the GPU and CPU are very
different), the conclusion here is similar to
Section~\ref{subsec:scalability}: The cost of communicating data and
tasks to and from the GPU imposes a higher task granularity to achieve
the same efficiency than running on the CPU, reducing the advantage at small task granularities of
very lightweight mechanisms such as those in MPI.

### 2019-07-25 6_related.tex
Apply Alex's updates.

Though smaller than full applications, mini-apps can be challenging to
implement to a level of quality sufficient for conducting comparative
studies between programming systems. The largest study we know of,
for the mini-app LULESH~\cite{LULESH13}, compares 7 programming
systems (Chapel, Charm++, CUDA, Lizst, Loci, OpenMP, and MPI), each of
which require a wholly separate, tuned implementation (in contrast to
Task Bench). Other
studies usually lack a comprehensive evaluation, even if multiple
implementations are available:

>>>>

Though smaller than full applications, mini-apps can be challenging to
implement to a level of quality sufficient for conducting comparative
studies between programming systems. The largest study we know of,
for the mini-app LULESH~\cite{LULESH13}, compares 7 programming
systems (Chapel, Charm++, CUDA, Lizst, Loci, OpenMP, and MPI), each of
which require a separate, tuned implementation (in contrast to
Task Bench). Other
studies usually lack a comprehensive evaluation, even if multiple
implementations are available:
